A Method for the Spectroscopic Inference of Stellar Parameters

### 2014-08-21 tex/paper.tex
ignor regions in GR

\begin{figure*}[!htb]
\begin{center}
\includegraphics{figs/matrix_compilation.pdf}
\caption{\textbf{Top}: A typical model fit and residual spectrum with a demonstrative region shaded in grey, showing the scale and structure of the residuals. \textbf{Left column}: A small inset of the covariance matrix corresponding to the gray region. Note that the colorbar scale changes with each inset in order to best illustrate the structure of the matrix. \textbf{Right column}: Each panel shows three random draws (gray) from a multivariate normal distribution using the covariance matrix in the left column. At the bottom of each panel is the envelope formed by 50 random draws (blue) overlaid with the actual residuals from the gray region. \textbf{First row}: White, Poisson-only noise ($\delta_{ij}\sigma_i$) does a poor job of reproducing both the scale and structure of a typical residual spectrum. \textbf{Second row}: The addition of a global kernel ($\mathcal{K}^{\rm g}$) yields random draws that closely approximate the structure and amplitude of the residuals, but miss the strong outlier line at 5202.2 \AA. \textbf{Third row}: Finally, adding in a local kernel ($\mathcal{K}^l$) at the location of the outlier produces random draws that completely match the structure of the residuals. Interestingly, note that the covariance matrix can produce random draws that have negative, positive, and even flat residual lines. The point is that with a non-trivial covariance matrix, the likelihood function can now accommodate the residuals generated from a typical spectroscopic fit. Stated differently, random draws from the likelihood function can now produce behavior that looks like the residuals, whereas before with only white noise it could not. All parameters of the covariance kernels are determined self-consistently along with the stellar parameters. }
\label{fig:matrix}
\end{center}
\end{figure*}

@@

\begin{figure*}[!htb]
\begin{center}
\includegraphics{figs/residuals_Kurucz_logg.pdf}
\caption{Kurucz WASP-14.}
\label{fig:residuals_Kurucz}
\end{center}
\end{figure*}

\begin{deluxetable}{lr@{$\pm$}l} 
\tablecaption{\label{table:Kurucz}WASP-14 {\sc CfA/Kurucz} results}
\tablehead{\colhead{Parameter} & \multicolumn{2}{c}{Value}}
\startdata
\cutinhead{Stellar parameters}
$T_{\rm eff}$ & 6516.8 & 12.6 K \\
$\log_{10} g$ & \multicolumn{2}{c}{4.29 dex} \\
$\Z$ & -0.27 & 0.01 dex \\
$v \sin i$ & 4.29 & 0.05 $\kms$\\
$v_z$ & -4.62 & 0.02 $\kms$ \\
$\log_{10} \Omega$ & -12.72 & 0.0004 \\
\cutinhead{Order 22 nuisance parameters}
$\cc{22}{0}$ & & \\
$\cc{22}{1}$ & & \\
$\cc{22}{2}$ & & \\
$\cc{22}{3}$ & & \\
$b_{22}$ & & \\
$a_{{\rm g}, 22}$ & & \\
$l_{22}$ & & \\
\cutinhead{Order 23 nuisance parameters}
$\cc{23}{0}$ & & \\
$\cc{23}{1}$ & & \\
$\cc{23}{2}$ & & \\
$\cc{23}{3}$ & & \\
$b_{23}$ & & \\
$a_{{\rm g}, 23}$ & & \\
$l_{23}$ & & \\
\cutinhead{Order 24 nuisance parameters}
$\cc{24}{0}$ & & \\
$\cc{24}{1}$ & & \\
$\cc{24}{2}$ & & \\
$\cc{24}{3}$ & & \\
$b_{24}$ & & \\
$a_{{\rm g}, 24}$ & & \\
$l_{24}$ & & \\
\enddata
\end{deluxetable}

@@

\begin{figure*}[!htb]
\begin{center}
  \includegraphics[width=0.5\textwidth]{figs/kurucz_triangle.pdf}
  \caption{The posterior probability function of the stellar parameters for WASP-14, an F star, as explored by the MCMC Gibbs sampler. These stellar parameters are marginalized over the Chebyshev ($\cheb$) and noise parameters ($\cov$). Figure generated with \texttt{triangle.py} \citep{foreman-mackey14}.
}
\label{fig:stellar_posterior}
\end{center}
\end{figure*}

>>>>

\begin{figure*}[!htb]
\begin{center}
\includegraphics{figs/matrix_compilation.pdf}
\caption{\textbf{Top}: A typical model fit and residual spectrum with a demonstrative region shaded in grey, showing the scale and structure of the residuals. \textbf{Left column}: A small inset of the covariance matrix corresponding to the gray region. Note that the colorbar scale changes with each inset in order to best illustrate the structure of the matrix. \textbf{Right column}: Each panel shows three random draws (gray) from a multivariate normal distribution using the covariance matrix in the left column. At the bottom of each panel are the one, two, and three sigma contours (orange) of 200 random draws overlaid with the actual residuals from the gray region. \textbf{First row}: White, Poisson-only noise ($\delta_{ij}\sigma_i$) does a poor job of reproducing both the scale and structure of a typical residual spectrum. \textbf{Second row}: The addition of a global kernel ($\mathcal{K}^{\rm g}$) yields random draws that closely approximate the structure and amplitude of the residuals, but miss the strong outlier line at 5202.2 \AA. \textbf{Third row}: Finally, adding in a local kernel ($\mathcal{K}^l$) at the location of the outlier produces random draws that completely match the structure of the residuals. Interestingly, note that the covariance matrix can produce random draws that have negative, positive, and even flat residual lines. The point is that with a non-trivial covariance matrix, the likelihood function can now accommodate the residuals generated from a typical spectroscopic fit. Stated differently, random draws from the likelihood function can now produce behavior that looks like the residuals, whereas before with only white noise it could not. All parameters of the covariance kernels are determined self-consistently along with the stellar parameters. }
\label{fig:matrix}
\end{center}
\end{figure*}

@@

\begin{figure*}[!htb]
\begin{center}
\includegraphics{figs/residuals_Kurucz_logg.pdf}
\caption{Kurucz WASP-14. One, two, and three sigma contours formed from 200 random draws from the covariance matrix.}
\label{fig:residuals_Kurucz}
\end{center}
\end{figure*}

\begin{figure}[!htb]
\begin{center}
  \includegraphics[width=0.5\textwidth]{figs/Kurucz_triangle.pdf}
  \caption{The posterior probability function of the stellar parameters for WASP-14, an F star, as explored by the MCMC Gibbs sampler. These stellar parameters are marginalized over the Chebyshev ($\cheb$) and noise parameters ($\cov$). Figure generated with \texttt{triangle.py} \citep{foreman-mackey14}.
}
\label{fig:stellar_posterior}
\end{center}
\end{figure}

\begin{deluxetable}{lr@{$\pm$}l} 
\tablecaption{\label{table:Kurucz}WASP-14 {\sc CfA/Kurucz} results}
\tablehead{\colhead{Parameter} & \multicolumn{2}{c}{Value}}
\startdata
\cutinhead{Stellar parameters}
$T_{\rm eff}$ & 6517.1 & 12.5 K \\
$\log_{10} g$ & \multicolumn{2}{c}{4.29 dex} \\
$\Z$ & -0.27 & 0.01 dex \\
$v \sin i$ & 4.29 & 0.05 $\kms$\\
$v_z$ & -4.620 & 0.016 $\kms$ \\
$\log_{10} \Omega$ & -12.7181 & 0.0004 \\
\cutinhead{Order 22 nuisance parameters}
$\log_{10} \cc{22}{0}$ &  0.0085 & 0.0005\\
$\cc{22}{1}$ & -0.0142 & 0.0015\\
$\cc{22}{2}$ & -0.0145 & 0.0017\\
$\cc{22}{3}$ & -0.0031 & 0.0011\\
\\
$b_{22}$ & 1.04 & 0.02 \\
$\log_{10} a_{{\rm g}, 22}$ & -14.63 & 0.020 $\textrm{erg}\;\textrm{cm}^{-2}\;\textrm{s}^{-1}\;\textrm{\AA}^{-1}$\\
$l_{22}$ & 7.54 & 0.77 $\kms$ \\

\cutinhead{Order 23 nuisance parameters}
$\log_{10} \cc{23}{0}$ & 0.0030 & 0.0006 \\
$\cc{23}{1}$ & -0.0133 & 0.0016 \\
$\cc{23}{2}$ & -0.0247 & 0.0014 \\
$\cc{23}{3}$ &  0.0012 &  0.0013\\
\\
$b_{23}$ & 1.01 & 0.02 \\
$\log_{10} a_{{\rm g}, 23}$ & -14.55 & 0.015 $\textrm{erg}\;\textrm{cm}^{-2}\;\textrm{s}^{-1}\;\textrm{\AA}^{-1}$\\
$l_{23}$ & 6.52 & 0.50 \\

\cutinhead{Order 24 nuisance parameters}
$\log_{10} \cc{24}{0}$ & \multicolumn{2}{c}{0.00} \\
$\cc{24}{1}$ & -0.0103 & 0.0016 \\
$\cc{24}{2}$ & -0.0112 & 0.0013\\
$\cc{24}{3}$ &  0.0002 & 0.0012\\
\\
$b_{24}$ & 1.02 & 0.02 \\
$\log_{10} a_{{\rm g}, 24}$ & -14.61 & 0.02 $\textrm{erg}\;\textrm{cm}^{-2}\;\textrm{s}^{-1}\;\textrm{\AA}^{-1}$\\
$l_{24}$ & 7.33 & 0.59 $\kms$ \\
\enddata
\end{deluxetable}

\begin{figure}[!htb]
\begin{center}
\includegraphics{figs/metacomparison.pdf}
\caption{Comparing all the posteriors.}
\label{fig:metacomparison}
\end{center}
\end{figure}

@@
